\documentclass[letterpaper,11pt,twocolumn]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{fontawesome5}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage{tgcursor}
\usepackage{geometry}
%\usepackage{fontspec} % Requires XeLaTeX or LuaLaTeX
%\setmainfont{TeX Gyre Termes} % Clear, readable serif font similar to Times

% -------------------- FONT AND MARGINS --------------------
\geometry{left=0.5in, right=0.5in, top=0.5in, bottom=0.5in, columnsep=20pt}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}

% Custom commands
\newcommand{\resumeItem}[1]{\item \small{#1}}
\newcommand{\resumeSubheading}[4]{
	\vspace{-2pt}\item \textbf{#1} \hfill #2 \\
	\textit{\small #3} \hfill \textit{\small #4} 
	\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% -------------------- START OF DOCUMENT --------------------
\begin{document}
	
	% Header
	\begin{center}
		{\LARGE \textbf{Yassine Machta}} \\[5pt]
		\href{mailto:machtayassine@gmail.com}{\faIcon{envelope} \underline{Gmail}} $\cdot$ 
		\href{https://github.com/MachtaYassine}{\faIcon{github} \underline{GitHub}} $\cdot$ 
		\href{https://www.linkedin.com/in/yassine-machta-a00307206/}{\faIcon{linkedin} \underline{LinkedIn}} $\cdot$ 
		\href{https://machtayassine.github.io}{\faIcon{chrome} \underline{Web page}}
	\end{center}
	
	\vspace{-10pt}
	\hrule
	\vspace{-17pt}
	
	% Education
	\section{Education}
	\begin{itemize}[leftmargin=*]
		\resumeSubheading
		{\href{https://www.ensae.fr/en}{ENSAE Paris}}{2021--2025}
		{Engineering Curriculum: Data Science, Statistics and Learning. GPA: 3.8}{}
		\resumeSubheading
		{\href{https://www.ip-paris.fr/}{Institut Polytechnique de Paris}}{2024--2025}
		{Master 2 Data Science}{}
        \resumeSubheading
		{\href{https://fermat.mon-ent-occitanie.fr/}{Lycée Pierre de Fermat}}{2019-2021}
		{Prepa MPSI/MP*}{}
	\end{itemize}
	
	% Work Experience
	\section{Work Experience}
	\begin{itemize}[leftmargin=*]
		\resumeSubheading
		{Research Intern}{Inria - \href{https://articulab.hcii.cs.cmu.edu/}{\underline{ARTICULAB}}, Paris}{May 2025 -- Nov 2025}{\textit{Supervised by: \href{https://scholar.google.com/citations?user=wkC9xHMAAAAJ&hl=en}{\underline{Cassell, J}} and \href{https://fr.linkedin.com/in/marius-le-chapelier-7694b5172}{\underline{Le Chapelier, M}}}} 
		%\vspace{5pt} \href{https://machtayassine.github.io/resume/Sony_LoR.pdf}{\underline{\textit{Letter of Recommendation}}}}
	
	\resumeItemListStart
	\resumeItem{Developed a real-time embedding/rule-based gesture retrieval baseline to enhance the believability of the Son of Sara Embodied Conversational Agent during user interactions.}
	\resumeItem{Moving toward learned, context-sensitive gesture generation.}
	\resumeItemListEnd
	
	\resumeSubheading
	{Research Intern}{\href{https://www.sony.com/en/SonyInfo/research/about/stuttgart-laboratory1/}{\underline{Sony R\&D}}, Stuttgart}{Jan 2024 -- Jun 2024}{\textit{Supervised by: \href{https://de.linkedin.com/in/zoltan-facius-6b424112}{\underline{Facius, Z}} and \href{https://de.linkedin.com/in/roberto-franceschi}{\underline{Franceschi, R}}} \vspace{5pt} \href{https://machtayassine.github.io/resume/Sony_LoR.pdf}{\underline{\textit{Letter of Recommendation}}}}
	
	\resumeItemListStart
	\resumeItem{Conducted experiments to evaluate the effect of uncontrolled environments on 3D reconstruction quality.}
	\resumeItem{Developed an automated pipeline for image preprocessing and 3D reconstruction.}
	\resumeItem{Created a web app to streamline mesh alignment and quality evaluation for engineering teams.}
	\resumeItemListEnd
	
	\resumeSubheading
	{Research Intern}{Inria - \href{https://team.inria.fr/simbiotx/}{\underline{SIMBIOTX}}, Saclay}{May 2023 -- Nov 2023}{\textit{Supervised by: \href{https://scholar.google.com/citations?user=tKRo0ewAAAAJ&hl=en}{\underline{Ali, O}} and \href{https://team.inria.fr/simbiotx/team-members/irene-vignon-clementel/}{\underline{Vignon-Clementel, I.}}}}
	
	\resumeItemListStart
	\resumeItem{Implemented topology-preserving losses for accurate 3D vessel segmentation.}
	\resumeItem{Performed statistical analysis of vessel tree morphometry and trained models on perfusion volumes.}
	\resumeItem{Published to MICCAI 2024 (ADSMI workshop), presented at poster session. See publications section for more details (\underline{\href{https://gitlab.inria.fr/simbiotx/LiverVesselSeg}{Code link}}).}

	\resumeItemListEnd
	
	\resumeSubheading
	{Data Science Intern}{Cour des Comptes, Paris}{Jun 2022 -- Sep 2022}{\textit{Supervised by: \href{https://fr.linkedin.com/in/paulgrignon}{\underline{Grignon, P}}}}
	
	\resumeItemListStart
	\resumeItem{Conducted a data analysis project in R to create an overview of the French Airport Network.}
	\resumeItem{Utilized descriptive statistics and cartography for data visualization.}
	\resumeItemListEnd
\end{itemize}

% Skills
\section{Skills}
\begin{itemize}[leftmargin=*]
	\item \textbf{Programming Languages:} Python (PyTorch, Scikit-learn/image, Selenium, pandas, Numpy, matplotlib), Git, Slurm, Kubernetes, ArgoCD, Docker. Currently learning CUDA/C++, Godot, and some JS/CSS.
\end{itemize}

% Projects
\section{Projects \& Labs}
\begin{itemize}[leftmargin=*]
	\resumeItem{\textbf{NLP and LLMs}: Finetuning LLMs using LoRA and DPO. Reimplemented "Unsupervised Multi Modal Translation" as a project to get familiar with transformers and multi modality.}
	\resumeItem{\textbf{RL} : Experimenting with RL in Godot engine (training agents to master Skull King and simple environment navigation)}
	\resumeItem{\textbf{Generative AI}: \underline{\href{https://github.com/MachtaYassine/GGSP-ALTEGRAD/tree/main}{Conditional graph generation}} and music sheet generation using diffusion and \underline{\href{https://colab.research.google.com/drive/1HT1E62hvaACGgLNt3xu5m51AO4m_fTxO}{Flow Matching}}}
	\resumeItem{\textbf{Finance}: Used Mistral API to set up analysis of the FOMC meeting minutes and speech data in order to attempt predicting signals (\underline{\href{https://colab.research.google.com/drive/1qGfLkEFJ_ta2YnJD77EUxmsFi99Svo5X?usp=sharing}{Link}})}
	\resumeItem{\textbf{GPU Programming}: GPU-accelerated Monte Carlo simulation for the Variance Gamma model. Rewrote and optimized GPU kernels for a given pytorch neural network to further optimize inference time.}
\end{itemize}

% Publications
\section{Publications}
\begin{itemize}[leftmargin=*]
	\resumeItem{\textbf{Machta, Y.}, Ali, O., Facque, A., Vlascenau A., Hakkakian, K., Golse N., Vignon-Clementel, I. (2024). "Improving 3D Liver Vessel Segmentation through Topology Preservation." In \textit{MICCAI ADSMI Workshop}, 2024. (\href{https://arxiv.org/abs/2411.15778}{\underline{Arxiv}}, \href{https://MachtaYassine.github.io/Papers/2024_ADSMI_poster.pdf}{\underline{Poster}} and \underline{\href{https://gitlab.inria.fr/simbiotx/LiverVesselSeg}{code}})}
\end{itemize}

% Extracurriculars
\section{Extracurricular Activities}
\begin{itemize}[leftmargin=*]
	\resumeSubheading
	{ENSAE English Debating Team}{2022--2023}{\href{https://www.frenchdebatingassociation.fr/\#fda}{\underline{FDA Tournament Winner}} }{}
	\resumeSubheading
	{Sports and Student Councils}{2022--2023}{Organized various events and activities at ENSAE Paris. Played on the volleyball team.}{}
\end{itemize}

% Languages
\section{Languages}
\begin{itemize}[leftmargin=*]
	\item \textbf{Arabic}: Native
	\item \textbf{French}: Native
	\item \textbf{English}: C1
\end{itemize}

\begin{flushright}
	\vspace{-4pt}
	\color{gray}
	Last built on \today.  \\
	Underlined text indicates clickable links. \\
	For the latest version, click \href{https://machtayassine.github.io/resume/resume_ymachta.pdf}{\underline{\textit{here}}}.
\end{flushright}

\end{document}